---
output:
  html_notebook: 
    highlight: tango
    theme: spacelab
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(forcats)
library(lme4)
library(langcog)
source("../util.R")
theme_set(theme_mikabr())
```

## Run 1

- 8 verbs (4 positive, 4 negative) and 8 properties (4 positive, 4 negative) randomly paired up such that there are 2 items of each positive/negative verb/property combination
- between subjects conditions (prior, positive, negative), each of 10 subjects in each condition sees all 8 items

```{r}
process_condition_1 <- function(condition) {
  
  read_csv(sprintf("run 1/results_%s.csv", condition)) %>%
    select(HITId, starts_with("Input"), starts_with("Answer")) %>%
    rename_(.dots = setNames(names(.),
                             gsub("^.*\\.(.*)$", "\\1", names(.)))) %>%
    gather(key, value, starts_with("prompt"), starts_with("code"),
           starts_with("response")) %>%
    separate(key, c("type", "trial"), sep = "_") %>%
    spread(type, value) %>%
    separate(code, c("verb_valence", "property_valence"), sep = ";") %>%
    mutate(response = as.numeric(response),
           trial = as.numeric(trial),
           condition = condition,
           property = sub(".*How likely is someone being (.*) to .* people\\?",
                          "\\1", prompt),
           verb = sub(".*How likely is someone being .* to (.*) people\\?",
                      "\\1", prompt),
           item = paste(verb, property, sep = " + "),
           verb_valence = sub("verb_(.*)", "\\1", verb_valence),
           property_valence = sub("property_(.*)", "\\1", property_valence))
  
}

conditions_1 <- c("prior", "positive", "negative")
results_1 <- map_df(conditions_1, process_condition_1)
results_1
```

```{r}
results_summary_1 <- results_1 %>%
  group_by(condition, verb_valence, property_valence) %>%
  summarise(response_mean = mean(response, na.rm = TRUE),
            response_se = sem(response, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(condition = as_factor(condition))
results_summary_1
```

```{r}
items_1 <- results_1 %>%
  filter(condition == "prior") %>%
  distinct(verb_valence, property_valence, verb, property) %>%
  group_by(verb_valence, property_valence) %>%
  summarise(verbs = paste(verb, collapse = ", "),
            properties = paste(property, collapse = ", "))
```

```{r, fig.height=3.5, fig.width=4}
ggplot(results_1, aes(x = condition, y = response, colour = item)) +
  facet_grid(verb_valence ~ property_valence, labeller = label_both) +
  geom_jitter(width = 0.1) +
  geom_segment(aes(y = response_mean, yend = response_mean,
                   x = as.numeric(condition) - 0.2,
                   xend = as.numeric(condition) + 0.2),
               data = results_summary_1, size = 1, colour = "black") +
  geom_rect(aes(xmin = as.numeric(condition) - 0.2,
                xmax = as.numeric(condition) + 0.2,
                ymin = response_mean + response_se * 1.96,
                ymax = response_mean - response_se * 1.96),
            colour = "grey", alpha = 0,
            data = results_summary_1, inherit.aes = FALSE) +
  geom_text(aes(label = properties), x = 2, y = 5.7, colour = "dark grey",
            family = "Open Sans", data = items_1) +
  geom_text(aes(label = verbs), x = 3.5, y = 3, colour = "dark grey",
            angle = -90, family = "Open Sans", data = items_1) +
  expand_limits(y = 5.7) +
  scale_colour_solarized(name = "") +
  theme(legend.position = "bottom")
```

## Run 2

- each combination of verb and property is an item (64 total)
- within subjects, each of 16 subjects sees 12 items, 4 from each condition

```{r}
results_2 <- read_csv("run 2/results_combined.csv") %>%
  select(HITId, starts_with("Input"), starts_with("Answer")) %>%
  rename_(.dots = setNames(names(.),
                           gsub("^.*\\.(.*)$", "\\1", names(.)))) %>%
  gather(key, value, starts_with("prompt"), starts_with("code"),
         starts_with("response")) %>%
  separate(key, c("type", "trial"), sep = "_") %>%
  spread(type, value) %>%
  mutate(response = as.numeric(response),
         trial = as.numeric(trial),
         property = sub(".*How likely is someone being (.*) to .* people\\?",
                        "\\1", prompt),
         verb = sub(".*How likely is someone being .* to (.*) people\\?",
                    "\\1", prompt),
         code_values = map(code, decode),
         condition = map_chr(code_values, ~.x[["condition"]]),
         verb_valence = map_chr(code_values, ~.x[["verb_valence"]]),
         property_valence = map_chr(code_values,
                                    ~.x[["property_valence"]])) %>%
  select(-code_values)
results_2
```

```{r}
results_summary_2 <- results_2 %>%
  group_by(condition, verb_valence, property_valence) %>%
  summarise(response_mean = mean(response, na.rm = TRUE),
            response_se = sem(response, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(condition = as_factor(condition))
results_summary_2
```

```{r}
items_2 <- results_2 %>%
  filter(condition == "prior") %>%
  distinct(verb_valence, property_valence, verb, property) %>%
  group_by(verb_valence, property_valence) %>%
  summarise(verbs = paste(sort(unique(verb)), collapse = ", "),
            properties = paste(sort(unique(property)), collapse = ", "))
```

```{r, fig.height=3, fig.width=4}
ggplot(results_2, aes(x = condition, y = response)) +
  facet_grid(verb_valence ~ property_valence, labeller = label_both) +
  geom_jitter(width = 0.1) +
  geom_segment(aes(y = response_mean, yend = response_mean,
                   x = as.numeric(condition) - 0.2,
                   xend = as.numeric(condition) + 0.2),
               data = results_summary_2, size = 1, colour = "black") +
  geom_rect(aes(xmin = as.numeric(condition) - 0.2,
                xmax = as.numeric(condition) + 0.2,
                ymin = response_mean + response_se * 1.96,
                ymax = response_mean - response_se * 1.96),
            colour = "grey", alpha = 0,
            data = results_summary_2, inherit.aes = FALSE) +
  geom_text(aes(label = properties), x = 2, y = 5.7, colour = "dark grey",
            family = "Open Sans", data = items_2) +
  geom_text(aes(label = verbs), x = 3.5, y = 3, colour = "dark grey",
            angle = -90, family = "Open Sans", data = items_2) +
  expand_limits(y = 5.7)
```

## Run 3

- 8 verbs (4 positive, 4 negative) and 8 properties (4 positive, 4 negative) manually paired up such that they subjectively fit well and there are 4 positive/positive items and 4 negative/negative items
- 6 filler items (3 high likelihood, 3 low likelihood)
- between subjects conditions (prior, positive, negative), each of 20 subjects in each condition sees all 8 items and all 6 fillers

```{r}
process_condition_3 <- function(condition) {
  
  read_csv(sprintf("run 3/results_%s.csv", condition)) %>%
    select(HITId, starts_with("Input"), starts_with("Answer")) %>%
    rename_(.dots = setNames(names(.),
                             gsub("^.*\\.(.*)$", "\\1", names(.)))) %>%
    gather(key, value, starts_with("prompt"), starts_with("code"),
           starts_with("response")) %>%
    separate(key, c("type", "trial"), sep = "_") %>%
    spread(type, value) %>%
    mutate(response = as.numeric(response),
           trial = as.numeric(trial),
           condition = condition,
           info = map(code, decode),
           type = map_chr(info,
                          ~ifelse(all(names(.x) == "filler_value"), "filler",
                                  "item")))
}

conditions_3 <- c("prior", "positive", "negative")
results_3 <- map_df(conditions_3, process_condition_3) %>%
  split(.$type)

results_filler_3 <- results_3$filler %>%
  mutate(filler_value = map_chr(info, ~.x[["filler_value"]]),
         correct = (filler_value == "high" & response >= 4) |
           (filler_value == "low" & response <= 2))

filler_filter_3 <- results_filler_3 %>%
  group_by(HITId) %>%
  summarise(n_correct = sum(correct, na.rm = TRUE)) %>%
  filter(n_correct >= 5)

results_item_3 <- results_3$item %>%
  filter(HITId %in% filler_filter_3$HITId) %>%
  mutate(verb_valence = map_chr(info, ~.x[["verb_valence"]]),
         property_valence = map_chr(info, ~.x[["property_valence"]]),
         item = sub(".*How likely is someone being (.*) to (.*) people\\?",
                    "\\1 \\+ \\2", prompt))

results_item_3
```

```{r}
results_summary_3 <- results_item_3 %>%
  group_by(condition, verb_valence, property_valence) %>%
  summarise(response_mean = mean(response, na.rm = TRUE),
            response_se = sem(response, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(condition = as_factor(condition))
results_summary_3
```

```{r}
ggplot(results_filler_3,
       aes(x = filler_value, y = response, colour = filler_value)) +
  geom_jitter(width = 0.1) +
  scale_colour_solarized()
```


```{r, fig.height=2.5, fig.width=4}
ggplot(results_item_3, aes(x = condition, y = response, colour = item)) +
  facet_wrap(~verb_valence + property_valence,
             labeller = label_both) +
  geom_jitter(width = 0.1) +
  geom_segment(aes(y = response_mean, yend = response_mean,
                   x = as.numeric(condition) - 0.2,
                   xend = as.numeric(condition) + 0.2),
               data = results_summary_3, size = 1, colour = "black") +
  geom_rect(aes(xmin = as.numeric(condition) - 0.2,
                xmax = as.numeric(condition) + 0.2,
                ymin = response_mean + response_se * 1.96,
                ymax = response_mean - response_se * 1.96),
            colour = "grey", alpha = 0,
            data = results_summary_3, inherit.aes = FALSE) +
  expand_limits(y = 5.7) +
  scale_colour_solarized(name = "") +
  theme(legend.position = "bottom")
```


## Run 4

- 24 verbs (12 positive, 12 negative) and 24 properties (12 positive, 12 negative) manually paired up such that they subjectively fit well and there are 12 positive/positive items and 12 negative/negative items
- 6 filler items, each with a high likelihood match and a low likelihood match (12 fillers total)
- between subjects conditions (prior, positive, negative), each of 30 subjects in each condition sees all 24 items and all 12 fillers
- participants only included if country is USA, native language is English, and number of fillers correct (rated 4 or 5 for high likelihood, rated 1 or 2 for low likelihood) is at least 10

```{r}
process_condition_4 <- function(condition) {
  
  read_csv(sprintf("run4/results_%s.csv", condition)) %>%
    select(HITId, starts_with("Input"), starts_with("Answer")) %>%
    rename_(.dots = setNames(names(.),
                             gsub("^.*\\.(.*)$", "\\1", names(.)))) %>%
    gather(key, value, starts_with("prompt"), starts_with("code"),
           starts_with("response")) %>%
    separate(key, c("type", "trial"), sep = "_") %>%
    spread(type, value) %>%
    mutate(response = as.numeric(response),
           trial = as.numeric(trial),
           condition = condition,
           info = map(code, decode),
           type = map_chr(info,
                          ~ifelse(all(names(.x) == "filler_value"), "filler",
                                  "item")))
}

conditions_4 <- c("prior", "positive", "negative")
results_4 <- map_df(conditions_4, process_condition_4) %>%
  split(.$type)

results_filler_4 <- results_4$filler %>%
  mutate(filler_value = map_chr(info, ~.x[["filler_value"]]),
         correct = (filler_value == "high" & response >= 4) |
           (filler_value == "low" & response <= 2))

filler_filter_4 <- results_filler_4 %>%
  group_by(HITId, country, english) %>%
  summarise(n_correct = sum(correct, na.rm = TRUE)) %>%
  filter(n_correct >= 10, country == "USA", english == "yes")

results_item_4 <- results_4$item %>%
  filter(HITId %in% filler_filter_4$HITId) %>%
  mutate(verb_valence = map_chr(info, ~.x[["verb_valence"]]),
         property_valence = map_chr(info, ~.x[["property_valence"]]),
         item = sub(".*How likely is someone being (.*) to (.*) people\\?",
                    "\\1 \\+ \\2", prompt))

results_item_4
```

```{r}
results_summary_4 <- results_item_4 %>%
  group_by(condition, verb_valence, property_valence) %>%
  summarise(response_mean = mean(response, na.rm = TRUE),
            response_se = sem(response, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(condition = as_factor(condition))
results_summary_4
```

```{r}
ggplot(results_filler_4,
       aes(x = filler_value, y = response, colour = filler_value,
           alpha = correct)) +
  geom_jitter(width = 0.1) +
  scale_colour_solarized()
```


```{r, fig.height=2.5, fig.width=4}
ggplot(results_item_4, aes(x = condition, y = response, colour = item)) +
  facet_wrap(~verb_valence + property_valence,
             labeller = label_both) +
  geom_jitter(width = 0.1) +
  geom_segment(aes(y = response_mean, yend = response_mean,
                   x = as.numeric(condition) - 0.2,
                   xend = as.numeric(condition) + 0.2),
               data = results_summary_4, size = 1, colour = "black") +
  geom_rect(aes(xmin = as.numeric(condition) - 0.2,
                xmax = as.numeric(condition) + 0.2,
                ymin = response_mean + response_se * 1.96,
                ymax = response_mean - response_se * 1.96),
            colour = "grey", alpha = 0,
            data = results_summary_4, inherit.aes = FALSE) +
  expand_limits(y = 5.7) +
  scale_colour_solarized(name = "") +
  theme(legend.position = "bottom")
```

```{r}
results_item_4 %>%
  split(.$verb_valence) %>%
  map(~lm(response ~ condition, data = .x)) %>%
  map(summary)
```

```{r}
results_item_4 %>%
  mutate(condition = fct_relevel(condition,
                                 c("prior", "positive", "negative")),
         scaled_response = scale(response)) %>%
  split(.$verb_valence) %>%
  map(~lmer(scaled_response ~ condition + (condition | HITId) + (condition | item),
            data = .x)) %>%
  map(summary)
```

